CAKE: Classification avec Kernel Embeddings \\ with Rademacher Complexity based Risk Bounds

### 2017-05-10 kernel_embedding_classifier.tex
Draft for special cases completed

\title{CAKE: Classification avec Kernel Embeddings \\ with Rademacher Complexity Bounds}

@@

\begin{abstract}
	We propose learning-theoretic bounds for learning the hyperparameters of kernel embeddings in the probabilistic multiclass classification context. Kernel embeddings are nonparametric methods to represent probability distributions directly through observed data in a reproducing kernel Hilbert space (RKHS). However, the problem of hyperparameter learning for kernel embeddings remains challenging, often relying on heuristics and domain specific knowledge. We begin by developing the kernel embedding classifier (KEC), and prove the stochastic convergence of its probabilistic predictions. We then prove that expected classification risk can be bounded by using a data dependent Rademacher complexity measure in the probably approximately correct (PAC) framework. We use this bound to propose a scalable kernel learning algorithm for probabilistic multiclass classification. Classification performance is benchmarked on standard UCI datasets. We further apply our proposed kernel learning algorithm to learn feature representations of a deep convolutional network, with improved accuracy as compared to the original network, demonstrating the generality of this approach.
\end{abstract}

@@

Data dependent risk bounds
\section{Introduction}
\label{sec:introduction}

@@

	Classification is perhaps one of the most important and thoroughly developed topics in machine learning and pattern recognition. Despite this, principled probabilistic classification on multiclass problems remains a difficult and challenging task, and most solutions tackle this issue rather indirectly. \note{Maybe elaborate on why multiclass problems are important and why we want probabilities estimates in our predictions.}

	Support vector classifiers (SVC) \citep{m2001introduction}, for example, are originally designed for non-probabilistic binary classification. Its simple and convex optimisation structure makes the model very attractive both theoretically and in practice. However, in order to cope with overfitting, slack constraints introduce hyperparameters for which training does not directly addressed except through standard cross-validation. In order to extend to multiclass scenarios, binary relevance such as one-against-all, one-against-one, or decision trees are used to build a multiclass classifier from multiple binary classifiers \citep{aly2005survey, hsu2002comparison}. There are also no straightforward way of assigning probabilities to SVC, and in many approaches probabilities are simply arbitrary score measures that has been normalised \citep{zadrozny2002transforming, franc2011support} (\note{Check this}). As such, while the original SVC formulation is certainly elegant and practical, its multitude of variants for probabilistic multiclass classification becomes rather convoluted.

	Within the similar domain of kernel-based classification, Gaussian process classifiers (GPC) \citep{rasmussen2006gaussian} are Bayesian models for which probability distributions are analysed in a principled manner, by constructing a latent model that is distributed as a Gaussian process. Nevertheless, the posterior class probabilities are not analytically tractable due to a non-Gaussian likelihood, which require methods such as Monte Carlo Markov Chain, expectation propagation, or variation inference to approximate. The GPC is also formulated as a binary classifier, and multiclass classification is either approached with binary relevance, or through introducing multiple latent functions that are to be squashed together through a softmax function if probabilistic outputs are to be retained.

	On the other end of the spectrum, parametric models are limited in its ability to grow in capacity as the dataset grows. Neural networks \citep{lecun2015deep} mitigates this issue by growing deep instead of wide so that each layer of the network extract meaningful features from the dataset. While they require large amounts of data in order to work, neural networks has been shown to be able to learn almost any complex function. However, the choice of the network architecture remains, and principled probabilistic methods are still undergoing active research. In domains where the available data is scarce, neural networks also become very difficult to design and train.

	In this paper, we propose a new and natural probabilistic multiclass classifier, the kernel embedding classifier (KEC), by casting multiclass classification problems into the kernel conditional embedding framework. Kernel embedding of probability distributions is a principled method for representing and manipulating general probability distributions, nonparametrically, in a reproducing kernel Hilbert space (RKHS) that is associated with a positive definite kernel. In this way, probability distributions do not need to be restricted to a parametric form, but instead fully expressed by the dataset in a nonparametric manner. In our approach, learning the classifier is done by learning a corresponding conditional embedding from data. We show that by placing a Kronecker delta kernel over the label space, decision probabilities and information entropies can be expressed as inner products in the correspondingly induced reproducing kernel Hilbert space, which can be consistently estimated from data using the conditional embedding framework. This method is very general and makes no distinction between binary and multiclass classification, presenting a unified and principled method for all probabilistic classification tasks.

	Being developed very generally for any choice of positive definite kernel $k$, the kernel embedding classifier places no limit on the family of kernels and the structure of its hyperparameters. In the current kernel embedding literature, there is no standard method to train the hyperparameters of a conditional embedding besides cross-validation. We further propose and develop a hyperparameter training scheme based on Rademacher complexity bounds, which appropriately balances the accuracy and generalisation capabilities of the classifier. We then develop a mini-batch stochastic gradient descent version of such a training procedure, which brings the notorious complexity of kernel methods that is cubic in the size of the dataset down to only cubic in the mini-batch size.

	With no restrictions on the type of kernel used for our classifier, we apply our training algorithm to learn kernels with deep convolutional features on standard image recognition tasks such as the MNIST dataset (\note{Mention more on experiments later when they are ready}). Specifically, we also test the performance of our classifier on ``high $d$, low $n$'' domains where the dimensionality of the problem is large compared to the number of observations, by restricting the size of the dataset to be less than the dimensionality of the problem.

	The fully nonparametric and probabilistic nature of the classifier also allows us to perform probabilistic inference on the inputs and, most interestingly, the hidden layers if using a deep kernel. Specifically, we can quantify and obtain the most representative input sample and hidden features of each class.

	In summary, our contributions are:

	\begin{itemize}
		\item A novel probabilistic multiclass classifier, the kernel embedding classifier (KEC), based on the theory and framework of kernel embedding of conditional distributions;
		\item Convergence guarantees on decision probability and information entropy estimates;
		\item A novel training algorithm based on minimising Rademacher complexity bounds of our kernel embedding classifier in a reproducing kernel Hilbert space, which balances classification performance and provides greater generalisation capabilities to the classifier;
		\item A mini-batch stochastic gradient descent variant of the above training algorithm, reducing training complexity from $O(n^{3})$ to $O(n_{b}^{3})$ in time and from $O(n^{2})$ to $O(n_{b}^{2})$ in space for a training dataset of size $n$ and a mini-batch size of $n_{b} << n$;
		\item A deep convolutional network extension to the kernel embedding classifier to learn a deep convolutional kernel embedding network for image recognition tasks; And,
		\item A methodology to perform probabilistic inference and mode reconstruction of the inputs and hidden feature layers, where we quantify and obtain the most representative sample and hidden features of each class.
	\end{itemize}

%	Most classification algorithms are binary classifiers, which can only handle the case where the output can only take instances from one of two classes. This is true for both SVM classifiers and GP classifiers. Part of the reason for that is that it works by learning a continuous latent function which basically represents the `strength' of one of the classes, and so it is really just inferring how likely an input is from class A and if not it would be from class B. To build a multiclass classifier, a simple approach is to train multiple binary classifiers to tell apart pairs of classes or sets of classes, and somehow fuse these results together. Notable examples are One Versus All (OVA) and All Versus All (AVA) approaches, as well as binary tree approaches.
%	
%	\href{http://www.vision.caltech.edu/malaa/publications/aly05multiclass.pdf}{Here} is a 2005 Survey which summarises the state-of-the-art in multiclass classification at the time, which supports what I just said above. It does not seem like the above scenario has fundamentally changed in the past 10+ years, although more sophisticated versions of what was described above has been proposed and tested.
%	
%	The idea I am proposing here is actually very simple and intuitive. Suppose the training data is $\{\bvec{x}_{i}, y_{i}\}_{i = 1}^{n}$ where $\bvec{x}_{i} \in \mathcal{X}, y_{i} \in \mathbb{N}_{m}$ for all $i \in \mathbb{N}_{n}$ with $\mathbb{N}_{m} := \{1, 2, \cdots, m\}$. To clarify, $n$ is the number of training points, $m$ is the number of classes involved, and $\mathcal{X}$ is usually a subset of some euclidean space $\mathbb{R}^{d}$ but it does not necessarily have to be so (which is an advantage in kernel methods in general, such as GPs). The idea is to use the kernel embedding framework to compute a conditional embedding empirically from those training points. We then show that class probabilities can be computed from the conditional embedding if we place a Kronecker delta kernel on the space of the outputs, $\mathbb{N}_{m}$. We show that these class probabilities estimates are consistent estimates of the true class probabilities. Furthermore, the corresponding Shannon information entropy estimate at each query input can be computed, in two different ways, and we explore the performance of each of these approaches. In this way, we propose a natural probabilistic classifier for multiclass classification.
%	
%	Computationally, this probabilistic classifier is to do the following. Given a set of training points $\{\bvec{x}_{i}, y_{i}\}_{i = 1}^{n}$ and a set of query inputs $\{\bvec{x}^{\star}_{i}\}_{i = 1}^{n^{\star}}$, our classifier can output $\hat{P}^{\star} = \{\hat{\bvec{p}}^{\star}_{i}\}_{i = 1}^{n^{\star}}$, the estimated class probabilities at the query points, and also $\bvec{h}^{\star} = \{\hat{h}^{\star}_{i}\}_{i = 1}^{n^{\star}}$, the estimated information entropy at the query points.
%	\\
%	\\
%
%	In \cref{sec:kernel_embedding_classifier}, by expressing decision probabilities as expectations of indicator functions in the RKHS, we derived a consistent estimate of the decision probabilities from an inner product between the empirical conditional embedding and the indicator function. Likewise, in \cref{sec:information_entropy}, by expressing information entropy as expected information in the RKHS, we derived a consistent estimate of the information entropy from an inner product between the empirical conditional embedding and the information function.

	Contrary to parametric models, kernel methods are nonparametric, and thus its model capacity grows with increasing data. Within a large enough family of kernels $k_{\theta}$, the kernel embedding classifier always has the capacity to shatter the training data and produce zero training error. Given that it has such capabilities, we instead focus on learning the simplest model that can generalise well to new test data. If we instead choose to train the classifier by adding some measure of training error as a penalty term to \eqref{eq:trace_norm_optimisation}, such as the training cross entropy loss, then it can very easily overfit by adapting its model capacity to the training data closely. The Rademacher complexity regularises this behaviour to learn a good balance between training error and unseen test error. In short, while parametric models have limited capacity and thus trying to learn to perform well on a training set to its best ability is a good indicator to test performance, nonparametric models has infinite capacity and need to learn not to exploit this capacity on training data and instead learn the simplest pattern it can to be able to infer about new test instances. Indeed, experiments show that KEC training usually starts with high training accuracy and very low cross entropy loss, and eventually learns the simplest model while maintaining that training accuracy, or even relaxes the training accuracy if the model is simply too complicated and unlikely to generalise well. That is, the training usually starts from a state of overfitting, and eventually learns simpler patterns and structures. This is in contrast with parameteric models, where training usually begins with low training accuracy that is to be improved as training continues.

@@

	On top of this, in practice we do not have access to the distribution $\mathbb{P}_{X Y}$ to analytically derive the conditional embedding. Instead, we have a finite collection of data points $\{x_{i}, y_{i}\} \in \mathcal{X} \times \mathcal{Y}$, $i \in \mathbb{N}_{n} := \{1, \dots, n\}$, for which the conditional embedding map $\mathcal{U}_{Y | X}$ can be estimated by
	\begin{equation}
		\hat{\mathcal{U}}_{Y | X} = \Psi (K + n \lambda I)^{-1} \Phi^{T},
	\label{eq:empirical_conditional_embedding}
	\end{equation}
	where $K := \{k(x_{i}, x_{j})\}_{i = 1, j = 1}^{n, n}$, $\Phi := \begin{bmatrix} \phi(x_{1}) & \dots & \phi(x_{n}) \end{bmatrix}$, $\Psi := \begin{bmatrix} \psi(y_{1}) & \dots & \psi(y_{n}) \end{bmatrix}$, $\phi(x) := k(x, \cdot)$, $\psi(y) := l(y, \cdot)$, and $\lambda$ is the regularisation parameter for the conditional operator \citep{song2013kernel}. We then define the empirical conditional embedding by $\hat{\mu}_{Y | X = x} := \hat{\mathcal{U}}_{Y | X} k(x, \cdot)$, which stochastically converges to the true conditional embedding $\mu_{Y | X = x}$ in the RKHS norm at a rate of $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$, under the assumption that $k(x, \cdot)$ is in the image of $C_{XX}$ \citet[Theorem 6]{song2009hilbert}. This allows us to approximate the conditional expectation \eqref{eq:conditional_expectation} with $\langle \hat{\mu}_{Y | X = x}, g \rangle$ instead, 
	\begin{equation}
		\mathbb{E}[g(Y) | X = x] \approx \langle \hat{\mu}_{Y | X = x}, g \rangle = \bvec{g}^{T} (K + n \lambda I)^{-1} \bvec{k}_{x},
	\label{eq:empirical_conditional_expectation}
	\end{equation}
	where $\bvec{g} := \{g(y_{i})\}_{i = 1}^{n}$ and $\bvec{k}_{x} := \{k(x_{i}, x\}_{i = 1}^{n}$, knowing that it would converge to the true expectation as $n$ increases for sufficiently small $\lambda$.

@@

	Let $p_{c}(x) := \mathbb{P}[Y = c | X = x]$ be the \textit{decision probability function} for class $c \in \mathbb{N}_{m}$, which is the probability of the class label $Y$ being $c$ when the example $X$ is $x$. We begin by writing this probability as an expectation of indicator functions,
	\begin{equation}
		p_{c}(x) := \mathbb{P}[Y = c | X = x] = \mathbb{P}[Y \in \{c\} | X = x] = \mathbb{E}[\mathbb{1}_{c}(Y) | X = x].
	\label{eq:decision_probability}
	\end{equation}	
	With $\mathbb{1}_{c} \in \mathcal{H}_{\delta}$, we let $g = \mathbb{1}_{c}$ in \eqref{eq:empirical_conditional_expectation} and $\bvec{1}_{c} := \{\mathbb{1}_{c}(y_{i})\}_{i = 1}^{n}$ to estimate the right hand side of \eqref{eq:decision_probability} by
	\begin{equation}
		\hat{p}_{c}(x) = f_{c}(x) := \bvec{1}_{c}^{T} (K + n \lambda I)^{-1} \bvec{k}_{x}.
	\label{eq:empirical_decision_probability}
	\end{equation}
	Therefore, the vector of empirical decision probability functions over the classes $c \in \mathbb{N}_{m}$ is
	\begin{equation}
		\hat{\bvec{p}}(x) = \bvec{f}(x) := \bvec{Y}^{T} (K + n \lambda I)^{-1} \bvec{k}_{x} \in \mathbb{R}^{m},
	\label{eq:empirical_decision_probability_vector}
	\end{equation}
	where $\bvec{Y} := \begin{bmatrix} \bvec{1}_{1} & \bvec{1}_{2} & \cdots & \bvec{1}_{m} \end{bmatrix} \in \{0, 1\}^{n \times m}$ is simply the one hot encoded labels $\{y_{i}\}_{i = 1}^{n}$.

	We proceed to show that the empirical decision probabilities \eqref{eq:empirical_decision_probability} is a consistent estimator for the actual decision probabilities as the dataset increases (See \cref{thm:probability_convergence} of \cref{app:convergence_theorems} for proof).
	\begin{theorem}[Uniform Convergence of Empirical Decision Probability Function]
		\label{thm:probability_convergence_copy}
		Assuming that $k(x, \cdot)$ is in the image of $C_{XX}$, the empirical decision probability function $\hat{p}_{c} : \mathcal{X} \to \mathbb{R}$ \eqref{eq:empirical_decision_probability} converges uniformly to the true decision probability $p_{c} : \mathcal{X} \to [0, 1]$ \eqref{eq:decision_probability} at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ for all $c \in \mathcal{Y} = \mathbb{N}_{m}$.
	\end{theorem}
	Finally, to perform classification at a query point $x^{\star} \in \mathcal{X}$, we simply take the class with the highest empirical decision probability, $\hat{y}^{\star} = \argmax_{c \in \mathbb{N}_{m}} \hat{p}_{c}(x^{\star})$.

@@

	If strict, valid probabilities are required for interpretation, visualisation, or other purposes, the probabilities can be clipped at zero then normalised to one - a procedure we refer to as \textit{clip-normalisation},
	\begin{equation}
		\tilde{p}_{c}(x) := \frac{\max\{\hat{p}_{c}(x), 0\}}{\sum_{j = 1}^{m} \max\{\hat{p}_{j}(x), 0\}}.
	\label{eq:probability_clip_normalise}
	\end{equation}
	Notice that for classification prediction, the argmax solution over the classes of the empirical decision probabilities \eqref{eq:empirical_decision_probability} and its clip-normalised version \eqref{eq:probability_clip_normalise} remain the same. Furthermore, since $\hat{p}_{c}(x)$ converges to valid probabilities $p_{c}(x)$ according to \cref{thm:probability_convergence_copy}, the effect of clip-normalisation reduces as $n$ increases such that $\tilde{p}_{c}(x)$ becomes very close to $\hat{p}_{c}(x)$ and $p_{c}(x)$.

\section{Hyperparameter Learning with Rademacher Complexity Bounds}
\label{sec:hyperparameter_learning}

@@

	\begin{algorithm}[tb]
		\caption{Kernel Embedding Classifier Training with Stochastic Gradient Descent}
		\label{alg:kernel_embedding_classifier_training}
		\begin{algorithmic}[1]
			\STATE {\bfseries Input:} kernel family $k_{\theta} : \mathcal{X} \times \mathcal{X} \to \mathbb{R}$, dataset $\{x_{i}, y_{i}\}_{i = 1}^{n}$, initial kernel parameters $\theta_{0}$, initial regularisation parameter $\lambda_{0}$, learning rate $\eta$, gradient error tolerance $\epsilon$, batch size $n_{b}$
			\STATE $\theta \leftarrow \theta_{0}$, $\lambda \leftarrow \lambda_{0}$
			\REPEAT
			\STATE Sample the next batch batch $\mathcal{I} \subseteq \mathbb{N}_{n}$, $| \mathcal{I} | = n_{b}$ \hspace{\fill} (For gradient descent, $n_{b} = n$ and $\mathcal{I} = \mathbb{N}_{n}$)
			\STATE $Y \leftarrow \{\delta(y_{i}, c) : i \in \mathcal{I}, c \in \mathbb{N}_{m}\} \hspace{\fill} \in \{0, 1\}^{n_{b} \times m}$
			\STATE $K_{\theta} \leftarrow \{k_{\theta}(x_{i}, x_{j}) : i \in \mathcal{I}, j \in \mathcal{I}\} \hspace{\fill} \in \mathbb{R}^{n_{b} \times n_{b}}$
			\STATE $L_{\theta, \lambda} \leftarrow \mathrm{cholesky}(K_{\theta} + n_{b} \lambda I_{n_{b}}) \hspace{\fill} \in \mathbb{R}^{n_{b} \times n_{b}}$
			\STATE $V_{\theta, \lambda} \leftarrow L_{\theta, \lambda}^{T} \backslash (L_{\theta, \lambda} \backslash Y) \hspace{\fill} \in \mathbb{R}^{n_{b} \times m}$
			\STATE $P_{\theta, \lambda} \leftarrow K_{\theta} V_{\theta, \lambda} \hspace{\fill} \in \mathbb{R}^{n_{b} \times m}$
			\STATE $q(\theta, \lambda) \leftarrow \frac{1}{n} \sum_{i = 1}^{n} \mathcal{L}_{\epsilon}((Y)_{i}, (P_{\theta, \lambda})_{i}) + 4 e \alpha(\theta) \sqrt{\mathrm{trace}(V_{\theta, \lambda}^{T} K_{\theta} V_{\theta, \lambda})}$ 
			\STATE $\theta \leftarrow \theta - \eta \frac{\partial q}{\partial \theta}(\theta, \lambda)$, $\lambda \leftarrow \lambda - \eta \frac{\partial q}{\partial \lambda}(\theta, \lambda)$ \hspace{\fill} (Or other gradient based updates such as Adam)
			\UNTIL{$\big\lVert \begin{bmatrix} \frac{\partial r}{\partial \theta}(\theta, \lambda)^{T} & \frac{\partial r}{\partial \lambda}(\theta, \lambda)^{T} \end{bmatrix}^{T} \big\rVert_{\infty} < \epsilon$} \hspace{\fill} (Stop if magnitude of all gradients are below $\epsilon$)
			\STATE {\bfseries Output:} kernel parameters $\theta$, regularisation parameter $\lambda$
		\end{algorithmic}
	\end{algorithm}

	\subsection{Mini-Batch Stochastic Gradient Descent}
	\label{sec:stochastic_gradient_descent}

@@

%	\note{Note that while it would certainly be great, the point of developing this kernel embedding classifier is not to beat other existing classification algorithms. The purpose is to develop a simple and elegant fully probabilistic multiclass classifier based on embedding the observed data directly into a reproducing kernel Hilbert space, with a quantifiable notion of model complexity. This is what we will aim to show here in the experiments as well. Below is just a summary of what has been done but has not been put together neatly yet.}
%	
%	\textbf{Experiments to Show}: We are aiming to do experiments on one toy dataset for illustration and visualisation, and on two real world datasets for benchmarking performance. So far, I am using the iris dataset for the toy dataset, and MNIST for one of the real world datasets. We should still find a third real world dataset that will really benefit from such a flexible nonparametric, probabilistic multiclass classifier.
%	
%	\begin{itemize}
%		\item A toy 2D classification tasks for visualising the properties and capabilities of the kernel embedding classifier. An simple example is the iris dataset, where we take only 2 attributes. There are three classes, so the probabilities can be visualised using RGB. We first use the first two attributes of the dataset, where the training examples are very non-separable. The point is to demonstrate that the kernel embedding classifier learns a simple and reasonable model that does not overfit, even though it has the capacity to shatter all the training data and have 100\% training accuracy. We then show that if we use the standard cross entropy loss as the objective for training, then we easily overfit the data.
%		\item We also show plots illustrating how the training objective, performance of the classifier, and the hyperparameters changes during the training procedure.
%		\item We then show results for training using SGD, which reveals that at a faster speed we arrive at the same solution as before.
%		\item We can then move on to actual real world datasets, like MNIST.
%		\item The MNIST dataset has 60000 training images and 10000 test images. So far I have results for only giving the first 500 training images to the kernel embedding classifier (much smaller than the dimensionality of the problem, which is 784), and it is to perform on the whole 10000 test images. We show that with a Gaussian kernel, we get around 82\% accuracy. Then, with a simple extension by adding three convolutional layers before give it to the Gaussian kernel, we get around 92\% accuracy. Of course, we also report the cross entropy loss. We do this with both gradient descent and SGD. We then compare this to support vector classifiers and Gaussian process classifiers. Then also compare this to state of the art convolutional neural networks with 500 observations for training data.
%		\item We can also use the learned length scale of a stationary kernel to visualise the most discriminative pixels in the image useful to the classifier.
%		\item More to come...
%	\end{itemize}

@@

\section{Information Entropy}
\label{sec:information_entropy}

@@

			\begin{equation}
			\begin{aligned}
				\hat{\mu}_{Y | X = x}(c) &= \langle l(c, \cdot), \hat{\mu}_{Y | X = x} \rangle \\
				&= \langle \psi(c), \hat{\mu}_{Y | X = x} \rangle \\
				&= \psi(c)^{T} \hat{\mu}_{Y | X = x} \\
				&= \psi(c)^{T} \hat{\mathcal{U}}_{Y | X} \phi(x) \\
				&= \psi(c)^{T} \Psi (K + n \lambda I)^{-1} \Phi^{T} \phi(x) \\
				&= \bvec{l}_{c}^{T} (K + n \lambda I)^{-1} \bvec{k}_{x}, \\
			\end{aligned}
			\end{equation}

@@

			\begin{equation}
				\hat{\mu}_{Y | X = x}(c) = \bvec{1}_{c}^{T} (K + n \lambda I)^{-1} \bvec{k}_{x} =: \hat{p}_{c}(x).
			\end{equation}
		\end{proof}

@@

	\subsection{Expected Risk Bounds}
	\label{thm:expected_risk_bound}

@@

	\subsection{More about the training objective}

>>>>

\title{CAKE: Classification avec Kernel Embeddings \\ with Rademacher Complexity based Risk Bounds}

@@

\begin{abstract}
	We propose learning-theoretic bounds for learning the hyperparameters of kernel embeddings in the probabilistic multiclass classification context. Kernel embeddings are nonparametric methods to represent probability distributions directly through observed data in a reproducing kernel Hilbert space (RKHS). However, the problem of hyperparameter learning for kernel embeddings remains challenging, often relying on heuristics and domain specific knowledge. We begin by developing the kernel embedding classifier (KEC), and prove the stochastic convergence of its probabilistic predictions. We then prove that expected classification error can be bounded with high probability using Rademacher complexity based risk bounds. We use this bound to propose a scalable kernel learning algorithm for probabilistic multiclass classification. Classification performance is benchmarked on standard UCI datasets. We further apply our proposed kernel learning algorithm to learn feature representations of a deep convolutional network, with improved accuracy as compared to the original network, demonstrating the generality of this approach.
\end{abstract}

@@

Data dependent risk bounds

\section{Introduction}
\label{sec:introduction}

@@

@@

	On top of this, in practice we do not have access to the distribution $\mathbb{P}_{X Y}$ to analytically derive the conditional embedding. Instead, we have a finite collection of data points $\{x_{i}, y_{i}\} \in \mathcal{X} \times \mathcal{Y}$, $i \in \mathbb{N}_{n} := \{1, \dots, n\}$, for which the conditional embedding map $\mathcal{U}_{Y | X}$ can be estimated by
	\begin{equation}
		\hat{\mathcal{U}}_{Y | X} = \Psi (K + n \lambda I)^{-1} \Phi^{T},
	\label{eq:empirical_conditional_embedding}
	\end{equation}
	where $K := \{k(x_{i}, x_{j})\}_{i = 1, j = 1}^{n, n}$, $\Phi := \begin{bmatrix} \phi(x_{1}) & \dots & \phi(x_{n}) \end{bmatrix}$, $\Psi := \begin{bmatrix} \psi(y_{1}) & \dots & \psi(y_{n}) \end{bmatrix}$, $\phi(x) := k(x, \cdot)$, $\psi(y) := l(y, \cdot)$, and $\lambda$ is the regularisation parameter for the conditional operator \citep{song2013kernel}. We then define the empirical conditional embedding by $\hat{\mu}_{Y | X = x} := \hat{\mathcal{U}}_{Y | X} k(x, \cdot)$, which stochastically converges to the true conditional embedding $\mu_{Y | X = x}$ in the RKHS norm at a rate of $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$, under the assumption that $k(x, \cdot)$ is in the image of $C_{XX}$ \cite[Theorem 6]{song2009hilbert}. This allows us to approximate the conditional expectation \eqref{eq:conditional_expectation} with $\langle \hat{\mu}_{Y | X = x}, g \rangle$ instead, 
	\begin{equation}
		\mathbb{E}[g(Y) | X = x] \approx \langle \hat{\mu}_{Y | X = x}, g \rangle = \bvec{g}^{T} (K + n \lambda I)^{-1} \bvec{k}(x),
	\label{eq:empirical_conditional_expectation}
	\end{equation}
	where $\bvec{g} := \{g(y_{i})\}_{i = 1}^{n}$ and $\bvec{k}(x) := \{k(x_{i}, x\}_{i = 1}^{n}$, knowing that it would converge to the true expectation as $n$ increases for sufficiently small $\lambda$.

@@

	Let $p_{c}(x) := \mathbb{P}[Y = c | X = x]$ be the \textit{decision probability function} for class $c \in \mathbb{N}_{m}$, which is the probability of the class label $Y$ being $c$ when the example $X$ is $x$. We begin by writing this probability as an expectation of indicator functions,
	\begin{equation}
		p_{c}(x) := \mathbb{P}[Y = c | X = x] = \mathbb{P}[Y \in \{c\} | X = x] = \mathbb{E}[\mathbb{1}_{c}(Y) | X = x].
	\label{eq:decision_probability}
	\end{equation}	
	With $\mathbb{1}_{c} \in \mathcal{H}_{\delta}$, we let $g = \mathbb{1}_{c}$ in \eqref{eq:empirical_conditional_expectation} and $\bvec{1}_{c} := \{\mathbb{1}_{c}(y_{i})\}_{i = 1}^{n}$ to estimate the right hand side of \eqref{eq:decision_probability} by
	\begin{equation}
		\hat{p}_{c}(x) = f_{c}(x) := \bvec{1}_{c}^{T} (K + n \lambda I)^{-1} \bvec{k}(x).
	\label{eq:empirical_decision_probability}
	\end{equation}
	Therefore, the vector of empirical decision probability functions over the classes $c \in \mathbb{N}_{m}$ is
	\begin{equation}
		\hat{\bvec{p}}(x) = \bvec{f}(x) := \bvec{Y}^{T} (K + n \lambda I)^{-1} \bvec{k}(x) \in \mathbb{R}^{m},
	\label{eq:empirical_decision_probability_vector}
	\end{equation}
	where $\bvec{Y} := \begin{bmatrix} \bvec{1}_{1} & \bvec{1}_{2} & \cdots & \bvec{1}_{m} \end{bmatrix} \in \{0, 1\}^{n \times m}$ is simply the one hot encoded labels $\{y_{i}\}_{i = 1}^{n}$.

	We proceed to prove that the empirical decision probabilities \eqref{eq:empirical_decision_probability} converges to the true decision probabilities with more data. We direct the reader to the supplementary material for proof.
	\begin{theorem}[Uniform Convergence of Empirical Decision Probability Function]
		\label{thm:probability_convergence_copy}
		Assuming that $k(x, \cdot)$ is in the image of $C_{XX}$, the empirical decision probability function $\hat{p}_{c} : \mathcal{X} \to \mathbb{R}$ \eqref{eq:empirical_decision_probability} converges uniformly to the true decision probability $p_{c} : \mathcal{X} \to [0, 1]$ \eqref{eq:decision_probability} at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ for all $c \in \mathcal{Y} = \mathbb{N}_{m}$.
	\end{theorem}
	Finally, to perform classification at a query point $x^{\star} \in \mathcal{X}$, we simply take the class with the highest empirical decision probability, $\hat{y}^{\star} = \argmax_{c \in \mathbb{N}_{m}} \hat{p}_{c}(x^{\star})$.

@@

	If strict, valid probabilities are required for interpretation, visualisation, or other purposes, the probabilities can be clipped at zero then normalised to one, a procedure we refer to as \textit{clip-normalisation},
	\begin{equation}
		\tilde{p}_{c}(x) := \frac{\max\{\hat{p}_{c}(x), 0\}}{\sum_{j = 1}^{m} \max\{\hat{p}_{j}(x), 0\}}.
	\label{eq:probability_clip_normalise}
	\end{equation}
	Notice that for classification prediction, the argmax solution over the classes of the empirical decision probabilities \eqref{eq:empirical_decision_probability} and its clip-normalised version \eqref{eq:probability_clip_normalise} remain the same. Furthermore, since $\hat{p}_{c}(x)$ converges to true probabilities $p_{c}(x)$ according to \cref{thm:probability_convergence_copy}, the effect of clip-normalisation reduces as $n$ increases such that $\tilde{p}_{c}(x)$ becomes very close to $\hat{p}_{c}(x)$ and $p_{c}(x)$.

\section{Learning with Rademacher Complexity based Risk Bounds}
\label{sec:hyperparameter_learning}

@@

	\begin{algorithm}[tb]
		\caption{KEC Hyperparameter Learning with Batch Stochastic Gradient Descent}
		\label{alg:kernel_embedding_classifier_training}
		\begin{algorithmic}[1]
			\STATE {\bfseries Input:} kernel family $k_{\theta} : \mathcal{X} \times \mathcal{X} \to \mathbb{R}$, dataset $\{x_{i}, y_{i}\}_{i = 1}^{n}$, initial kernel parameters $\theta_{0}$, initial regularisation parameter $\lambda_{0}$, learning rate $\eta$, gradient error tolerance $\epsilon$, batch size $n_{b}$
			\STATE $\theta \leftarrow \theta_{0}$, $\lambda \leftarrow \lambda_{0}$
			\REPEAT
			\STATE Sample the next batch $\mathcal{I} \subseteq \mathbb{N}_{n}$, $| \mathcal{I} | = n_{b}$ \hspace{\fill} (For gradient descent, $n_{b} = n$ and $\mathcal{I} = \mathbb{N}_{n}$)
			\STATE $Y \leftarrow \{\delta(y_{i}, c) : i \in \mathcal{I}, c \in \mathbb{N}_{m}\} \hspace{\fill} \in \{0, 1\}^{n_{b} \times m}$
			\STATE $K_{\theta} \leftarrow \{k_{\theta}(x_{i}, x_{j}) : i \in \mathcal{I}, j \in \mathcal{I}\} \hspace{\fill} \in \mathbb{R}^{n_{b} \times n_{b}}$
			\STATE $L_{\theta, \lambda} \leftarrow \mathrm{cholesky}(K_{\theta} + n_{b} \lambda I_{n_{b}}) \hspace{\fill} \in \mathbb{R}^{n_{b} \times n_{b}}$
			\STATE $V_{\theta, \lambda} \leftarrow L_{\theta, \lambda}^{T} \backslash (L_{\theta, \lambda} \backslash Y) \hspace{\fill} \in \mathbb{R}^{n_{b} \times m}$
			\STATE $P_{\theta, \lambda} \leftarrow K_{\theta} V_{\theta, \lambda} \hspace{\fill} \in \mathbb{R}^{n_{b} \times m}$
			\STATE $q(\theta, \lambda) \leftarrow \frac{1}{n} \sum_{i = 1}^{n} \mathcal{L}_{\epsilon}((Y)_{i}, (P_{\theta, \lambda})_{i}) + 4 e \alpha(\theta) \sqrt{\mathrm{trace}(V_{\theta, \lambda}^{T} K_{\theta} V_{\theta, \lambda})}$
			\STATE $\theta \leftarrow \theta - \eta \frac{\partial q}{\partial \theta}(\theta, \lambda)$, $\lambda \leftarrow \lambda - \eta \frac{\partial q}{\partial \lambda}(\theta, \lambda)$ \hspace{\fill} (Or other gradient based updates such as Adam)
			\UNTIL{$\big\lVert \begin{bmatrix} \frac{\partial r}{\partial \theta}(\theta, \lambda)^{T} & \frac{\partial r}{\partial \lambda}(\theta, \lambda)^{T} \end{bmatrix}^{T} \big\rVert_{\infty} < \epsilon$} \hspace{\fill} (Stop if magnitude of all gradients are below $\epsilon$)
			\STATE {\bfseries Output:} kernel parameters $\theta$, regularisation parameter $\lambda$
		\end{algorithmic}
	\end{algorithm}

	\subsection{Batch Stochastic Gradient Descent}
	\label{sec:stochastic_gradient_descent}

@@

@@

\section{Information Entropy}
\label{app:information_entropy}

@@

			\begin{equation}
			\begin{aligned}
				\hat{\mu}_{Y | X = x}(c) &= \langle l(c, \cdot), \hat{\mu}_{Y | X = x} \rangle \\
				&= \langle \psi(c), \hat{\mu}_{Y | X = x} \rangle \\
				&= \psi(c)^{T} \hat{\mu}_{Y | X = x} \\
				&= \psi(c)^{T} \hat{\mathcal{U}}_{Y | X} \phi(x) \\
				&= \psi(c)^{T} \Psi (K + n \lambda I)^{-1} \Phi^{T} \phi(x) \\
				&= \bvec{l}_{c}^{T} (K + n \lambda I)^{-1} \bvec{k}(x), \\
			\end{aligned}
			\end{equation}

@@

			\begin{equation}
				\hat{\mu}_{Y | X = x}(c) = \bvec{1}_{c}^{T} (K + n \lambda I)^{-1} \bvec{k}(x) =: \hat{p}_{c}(x).
			\end{equation}
		\end{proof}

@@

	\subsection{Expected Risk Bounds}
	\label{app:expected_risk_bounds}

@@
